Global adjoint tomography -- Model GLAD-M25 \\ Supplementary Material

### 2020-02-19 response_to_reviewers.tex

\rev{(ii) The strength of structure in the models is for a large part determined by regularization. As shown in Ritsema et al. 2011 we can change the amplitude of S40 (and the width of the resolution kernels) by changing the damping without compromising the data fit significantly. Comparing amplitudes of structures from different models without considering resolution differences is a tricky thing.}

\response{We agree that the amplitude of classical tomographic models heavily depend on subjective decisions of damping, and other factors while it is required for the interpretation of the thermochemical structure and dynamics of the mantle. Unfortunately we cannot make a reliable assessment of amplitudes. All we can say is that our results show significant increase in amplitudes compared to M15 specifically on plume and slab structures where our non-linear gradient-based optimization does not involve the damping factor.}

\rev{q) In Figure 18 I suggest to include the model by Krischer et al. (JGR; 2018). Model US22 is perhaps not that useful in the context of this comparison since it is based on a similar modeling approach and data set as M25.}

\response{We could use Krischer et al. (2018) however looks like it is smoother than US22. Our point is that we have started achieving the resolution of continental-scale studies in global inversions wherever we have dense coverage.}

\rev{r) Since SL2013NA (a ``ray'' model) doesn't appear too different from M25 it is not clear from the visual comparison) whether modeling improvements (i.e., better theories) matter.
(Note that I suspect they do matter for surface waves because your variance reduction is large for the surface wave data -- see my point 1).}

\response{Not sure if they are very similar, in fact they show strong discrepancies below 100 km. }

\rev{s) The differences among the models at depths larger than 300 km in Figure 18 is striking.
The authors draw the reader's attention to anomalies with well-understood tectonic origins but at face value the images are really very different especially for US22 (and M25) and SL2013NA.
The latter model is based on a large set of overtone surface wave data that should sample the MTZ very well. The misfit reduction obtained for the 40-100 s body + surface waves (presumably waveform segments after SS and before the fundamental mode surface wave) is relatively poor, so perhaps the MTZ in M25 is still poorly resolved (or S362 was an excellent model to begin with).
At any rate, this need further discussion. Transition zone resolution is still a sticky point and is important for understand convective flow.}

\response{Due to our cross-correlation measurements higher-modes may well be underrepresented in the current inversions. We are working on other misfit functions to effectively incorporate smaller-amplitude signals (e.g., Bozdag et al. 2011, Yuan et al. 2020) together with better window-selection strategies.}

\rev{t) Figure 19. Perhaps include SL2013sv and the model by Rickers et al. (EPSL; 2013).
}
\response{Rickers et al. model is more focusing on the upper mantle thus we chose to compare the Icelandic plume to those in other global models to see the continuation of the plume. However we now discuss it in the revised manuscript.}

\response{Note that based on comments from the other reviewers and the editor, we have moved
all model comparisons to the SOM, except for the plumes and slabs figures.
We have added a figure in which we directly compare M15 and M25 for a few key locations.}
